Child care situation of working mothers in Ghana 1998

### 2022-04-03 outputs/paper.Rmd
Fix errors

This was a part of the worldwide Demographic and Health Surveys (DHS) programme, and the GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire. All the questionnaires were modified to account for the situation in Ghana.

The survey was conducted in person. The interview staff were first trained for a period of three weeks. It was conducted by a total of 14 teams, comprising a team supervisor, a field editor, three interviewers and a driver. The response rate was 97% for individual men and women selected. Non-response was mainly due to inability to find the selected interviewee at home. Repeated callbacks were made to try to reach the selected respondents. The results of the survey did not disclose any confidential information that might identify the respondents. The survey was a voluntary one but it is unclear if the purpose of the survey explained to the respondents for them to make an informed decision.

@@

```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions", fig.width=8, fig.height=7}
# make dataset into long format
# recode names
child <- region %>% 
  select(-c(character, total, caretaker_missing)) %>% 
  pivot_longer(!background, names_to = "variable", values_to = "percentage") %>% 
  mutate(
    variable = factor(variable, 
                      levels = c('caretaker_respondent',
                                 'caretaker_partner',
                                 'caretaker_other_relative',
                                 'caretaker_neighbor',
                                 'caretaker_hired',
                                 'caretaker_child_in_school',
                                 'caretaker_other_female_child',
                                 'caretaker_other_male_child',
                                 'caretaker_not_worked_since_birth',
                                 'caretaker_other')
    )
  ) %>%
  mutate(variable = recode(variable,
                           'caretaker_respondent' = 'respondent',
                           'caretaker_partner' = 'partner',
                           'caretaker_other_relative' = 'other relative',
                           'caretaker_other_male_child' = 'other male child',
                           'caretaker_other_female_child' = 'other female child',
                           'caretaker_other' = 'other',
                           'caretaker_not_worked_since_birth' = 'not worked since birth',
                           'caretaker_neighbor' = 'neighbor',
                           'caretaker_hired' = 'hired help',
                           'caretaker_child_in_school' = 'schooling',
                           'no_child_under_six' = 'no child under six',
                           'one_more_child_under_six' = 'one or more child under six',
                           'number_of_employed_women' = 'number of employed women'))

@@

```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
# looking at the number of employed women selected in the different administrative regions
# with the child under six
child %>% 
  filter(variable == "no child under six" | variable == "one or more child under six") %>% 
  ggplot(aes(x = background,
             y = percentage,
             fill = variable)) +
  geom_bar(stat = 'identity', position = "dodge", width = 0.8) +
  labs(x = "Administrative regions",
       y = "Percentage",
       fill = "Child under six") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip() 
```

>>>>

@@

```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions", fig.width=8, fig.height=7}
# make dataset into long format
# recode names
child <- region %>% 
  select(-c(character, total, caretaker_missing)) %>% 
  pivot_longer(!background, names_to = "variable", values_to = "percentage") %>% 
  mutate(
    variable = factor(variable, 
                      levels = c('caretaker_respondent',
                                 'caretaker_partner',
                                 'caretaker_other_relative',
                                 'caretaker_neighbor',
                                 'caretaker_hired',
                                 'caretaker_child_in_school',
                                 'caretaker_other_female_child',
                                 'caretaker_other_male_child',
                                 'caretaker_not_worked_since_birth',
                                 'caretaker_other',
                                 'no_child_under_six',
                                 'one_more_child_under_six')
    )
  ) %>%
  mutate(variable = recode(variable,
                           'caretaker_respondent' = 'respondent',
                           'caretaker_partner' = 'partner',
                           'caretaker_other_relative' = 'other relative',
                           'caretaker_other_male_child' = 'other male child',
                           'caretaker_other_female_child' = 'other female child',
                           'caretaker_other' = 'other',
                           'caretaker_not_worked_since_birth' = 'not worked since birth',
                           'caretaker_neighbor' = 'neighbor',
                           'caretaker_hired' = 'hired help',
                           'caretaker_child_in_school' = 'schooling',
                           'no_child_under_six' = 'no child under six',
                           'one_more_child_under_six' = 'one or more child under six',
                           'number_of_employed_women' = 'number of employed women'))

@@

```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
# looking at the number of employed women selected in the different administrative regions
# with the child under six
child %>%
  filter(variable=='no child under six'|variable=='one or more child under six') %>% 
  ggplot(aes(x = background,
             y = percentage,
             fill = variable)) +
  geom_bar(stat = 'identity', position = "dodge", width = 0.8) +
  labs(x = "Administrative regions",
       y = "Percentage",
       fill = "Child under six") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip() 
```
